---
title: "Kunlei Lian's CV"
author: Kunlei Lian
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> kunlei1987@gmail.com
- <i class="fa fa-github"></i> github.com/kunlei
- <i class="fa fa-link"></i> [kunlei.github.io](http://kunlei.github.io/)




Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.




Main
================================================================================

Kunlei Lian {#title}
--------------------------------------------------------------------------------

### Sr. Data Scientist (Operations Research) at Walmart Labs.
```{r}
intro_text <- ""

cat(sanitize_links(intro_text))
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Ph.D. in Industrial Engineering

University of Arkansas

Arkansas, USA

2017 - 2012

- Studied the impact of improving service consistency in vehicle routing problems using multi-objective heuristic and branch-and-price algorithms.

### M.S. in Industrial Engineering

Huazhong University of Science and Technology

Wuhan, China

2012 - 2009

- Developed heuristic algorithms to solve job shop scheduling and assembly line balancing problems in manufacturing systems.

### B.S. in Industrial Engineering

Huazhong University of Science and Technology

Wuhan, China

2009 - 2005



Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Sr. Data Scientist (Operations Research)

Walmart Inc.

AR, USA

Present - 2019.01

- Developed a profiling application consisting of frontend UI and backend algorithm to facilitate item slotting decisions within all grocery distribution centers across Walmart U.S.
- Upgraded legacy optimization engine to support Walmart's ocean procurement process for 2020. Achieved *$30 million* operational cost savings, significant labor hour reduction and improved global supply chain balance and stability.

::: aside
Skills used: Html, CSS, JavaScript, React, Java, SpringBoot, SQL
:::

### Data Scientist (Operations Research)

Walmart Inc.

AR, USA

2019.01 - 2016.08

- Built a column-generation-based optimization engine within a rolling horizon framework to assign drivers to tractors with the objective of maximizing tractor utilization and minimizing driver split-seat. Achieved *$4 million* labor cost savings and *$8 million* operational cost savings annually.
- Migrated legacy truckload optimization COBOL code to Java, reducing data processing time from 10 minutes to 10 seconds. Developed heuristic algorithms to solve instances with large amount of orders, resulting in saving of 14 trucks daily.
- Implemented a column-generation-based optimization engine to estimate store-level customer purchase probability based on historical transaction data. Built a MIP engine to decide optimal offer set for each category at store level. 

::: aside
Skills used: Java, CPLEX, MIP, column generation
:::

### Global Business Processes Intern

Walmart Inc.

AR, USA

2016.08 - 2016.05

- Worked on implementation and validation of next generation inventory optimization model for Walmart U.S. and achieved 8% improvement over the current system during pilot store testing. Lead data platform migration from Teradata to Hadoop, responsible for data ETL and Hive query implementation.

::: aside
Skills used: R, SQL, Hive, Shell Scripting
:::

### Operations Research Analyst Intern

China Railway Siyuan Survey and Design Group CO., LTD.

Wuhan, China

2009.08 - 2009.05

- Implemented a metaheuristic algorithm to identify the optimal maintenance warehouse locations within a railway network.


Patents {data-icon=ribbon}
-------------------------------------------------------------------------------

### Dynamic Data Driven Store Front End Layout Optimization

with Jingying Zhang; Dong Xu; Tyler Nicholas; Jackie Guan; Fan Wang; Shuohao Wu

Filed

- Walmart Inc. has thousands of physical stores and an essential functionality of a store is front end checkout station layout design. This invention aims to recommend an optimal layout design that can be sustainably applied across yearly customer traffic without incurring large line length and long waiting time for Walmart store customers.


### GPU-enabled Safety Stock Optimization Engine

with Shuohao Wu, Richard Ulrich, Dong Xu, Jingying Zhang, Clifford Bolinger, Jackie Guan

Filed

- This invention aims to provide a solution on the optimal safety stock level settings across the chain such that the total inventory cost can be reduced, while not affecting the total sales. It leverages simulation and machine learning techniques powered by GPU computation.

Publications {data-icon=book}
--------------------------------------------------------------------------------

### An improved multi-directional local search algorithm for the multi-objective consistent vehicle routing problem.

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

N/A

N/A

IISE Transactions. 2016. 48(10): 975 – 992.

### Applying modified colonial competitive algorithm to solve minimal hitting set problems.

Chuanjun Zhu, Jing Cao, Chaoyong Zhang and *Kunlei Lian*

N/A

N/A

China Mechanical Engineering. 2015. 26(07): 917- 923.

### A modified colonial competitive algorithm for the mixed-model U-line balancing and sequencing problem.

*Kunlei Lian*, Chaoyong Zhang, Liang Gao and Xinyu Shao

N/A

N/A

International Journal of Production Research. 2012. 50(18): 5117 – 5131.


```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>

")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


