---
title: "Kunlei Lian's Resume"
author: Kunlei Lian
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> kunlei.lian@gmail.com
- <i class="fa fa-github"></i> github.com/kunlei
- <i class="fa fa-link"></i> [kunlei.github.io](http://kunlei.github.io/)




Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.




Main
================================================================================

Kunlei Lian {#title}
--------------------------------------------------------------------------------

### Staff Data Scientist (Operations Research) at Walmart Labs.
```{r}
intro_text <- ""

cat(sanitize_links(intro_text))
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Ph.D. in Industrial Engineering

University of Arkansas

Arkansas, USA

2017 - 2012

- Studied the impact of improving service consistency in vehicle routing problems using multi-objective heuristic and branch-and-price algorithms.

### M.S. in Industrial Engineering

Huazhong University of Science and Technology

Wuhan, China

2012 - 2009

- Developed heuristic algorithms to solve job shop scheduling and assembly line balancing problems in manufacturing systems.

### B.S. in Industrial Engineering

Huazhong University of Science and Technology

Wuhan, China

2009 - 2005



Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Staff Data Scientist -- Operations Research

Walmart Inc.

AR, USA

Present - 2020.01

- Optimization engine design and development.

::: aside
Skills used: C++, Java
:::


### Sr. Data Scientist -- Operations Research

Walmart Inc.

AR, USA

2020.01 - 2019.01

- Developed a profiling application consisting of frontend UI and backend algorithm to facilitate item slotting decisions within all grocery distribution centers across Walmart U.S.
- Upgraded legacy optimization engine to support Walmart's ocean procurement process for 2020. Achieved *$30 million* operational cost savings, significant labor hour reduction and improved global supply chain balance and stability.

::: aside
Skills used: Html, CSS, JavaScript, React, Java, SpringBoot, SQL
:::

### Data Scientist -- Operations Research

Walmart Inc.

AR, USA

2019.01 - 2016.08

- Built a column-generation-based optimization engine within a rolling horizon framework to assign drivers to tractors with the objective of maximizing tractor utilization and minimizing driver split-seat. Achieved *$4 million* labor cost savings and *$8 million* operational cost savings annually.
- Migrated legacy truckload optimization COBOL code to Java, reducing data processing time from 10 minutes to 10 seconds. Developed heuristic algorithms to solve instances with large amount of orders, resulting in saving of 14 trucks daily.
- Implemented a column-generation-based optimization engine to estimate store-level customer purchase probability based on historical transaction data. Built a MIP engine to decide optimal offer set for each category at store level. 

::: aside
Skills used: Java, CPLEX, MIP, column generation
:::

### Global Business Processes Intern

Walmart Inc.

AR, USA

2016.08 - 2016.05

- Worked on implementation and validation of next generation inventory optimization model for Walmart U.S. and achieved 8% improvement over the current system during pilot store testing. Lead data platform migration from Teradata to Hadoop, responsible for data ETL and Hive query implementation.

::: aside
Skills used: R, SQL, Hive, Shell Scripting
:::

### Operations Research Analyst Intern

China Railway Siyuan Survey and Design Group CO., LTD.

Wuhan, China

2009.08 - 2009.05

- Implemented a metaheuristic algorithm to identify the optimal maintenance warehouse locations within a railway network.


Patents {data-icon=ribbon}
-------------------------------------------------------------------------------

### GPU-enabled Safety Stock Optimization Engine

Filed with Shuohao Wu, Richard Ulrich, Dong Xu, Jingying Zhang, Clifford Bolinger, Jackie Guan

N/A

N/A


- This invention aims to provide a solution on the optimal safety stock level settings across the chain such that the total inventory cost can be reduced, while not affecting the total sales. It leverages simulation and machine learning techniques powered by GPU computation.

Journal Publications {data-icon=book}
--------------------------------------------------------------------------------

### An improved multi-directional local search algorithm for the multi-objective consistent vehicle routing problem.

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

N/A

N/A

IISE Transactions. 2016. 48(10): 975 – 992.

### Applying modified colonial competitive algorithm to solve minimal hitting set problems.

Chuanjun Zhu, Jing Cao, Chaoyong Zhang and *Kunlei Lian*

N/A

N/A

China Mechanical Engineering. 2015. 26(07): 917- 923.

### A modified colonial competitive algorithm for the mixed-model U-line balancing and sequencing problem.

*Kunlei Lian*, Chaoyong Zhang, Liang Gao and Xinyu Shao

N/A

N/A

International Journal of Production Research. 2012. 50(18): 5117 – 5131.

### Integrated process planning and scheduling using an imperialist competitive algorithm.

*Kunlei Lian*, Chaoyong Zhang, Liang Gao and Xinyu Li

N/A

N/A

International Journal of Production Research. 2012. 50(15): 4326 – 4343.

### Optimization of process planning with various flexibilities using an imperialist competitive algorithm.

*Kunlei Lian*, Chaoyong Zhang, Xinyu Shao and Liang Gao

N/A

N/A

International Journal of Advanced Manufacturing Technology. 2012. 59(5-8): 815 – 828.


### A multi-dimensional tabu search algorithm for the optimization of process planning.

*Kunlei Lian*, Chaoyong Zhang, Xinyu Shao and Yaohui Zeng

N/A

N/A

Science China Technological Sciences. 2011. 54(12): 3211 – 3219.

### A cooperative simulated annealing algorithm for the optimization of process planning.

*Kunlei Lian*, Chaoyong Zhang, Liang Gao, Shaotan Xu and Yi Sun

N/A

N/A

Advanced Materials Research. 2011. 181: 489 – 494.

### An adaptive ant colony optimization for solving assembly line balancing problem.

Fuping Deng, Chaoyong Zhang, *Kunlei Lian* and Shaotan Xu

N/A

N/A

China Mechanical Engineering. 2011. 22(16): 1949 - 1953, 1959.


### Application of bee colony optimization algorithm in warehouse facility location of rail transit network.

Kun Zhang, Hui Liu, *Kunlei Lian*

N/A

N/A

Modern Urban Transit. 2011. 1:63-66.


### An improved genetic algorithm for multi-objective dynamic scheduling optimization.

Kunlei Lian, Chaoyong Zhang, Liang Gao and Chaoyang Zhang, 

N/A

N/A


Machine Design and Manufacturing Engineering. 2010. 3:13 - 17, 21

Conference Publications {data-icon=globe}
--------------------------------------------------------------------------------

### A Hybrid Colonial Competitive Algorithm for the Integrated Process Planning and Scheduling Problem.

Yibo Wei, Yuxiang Lian, Leilei Meng, Yifeng Wang, Chaoyong Zhang, *Kunlei Lian*

N/A

N/A

In: 2020 International Conference on Urban Engineering and Management Science

### A hybrid honey-bees mating optimization algorithm for assembly sequence planning problem.

Biao Yuan, Chaoyong Zhang, *Kunlei Lian* and Xinyu Shao

N/A

N/A

In: Proceedings of the 8th International Conference on Natural Computation, May 29-31, 2012. 1135-1140

### Single row facility layout problem using an imperialist competitive algorithm.

*Kunlei Lian*, Chaoyong Zhang, Liang Gao and Xinyu Shao

N/A

N/A


In: Proceedings of the 41st International Conference on Computers & Industrial Engineering, October 23-26, 2011.

### New high performing hybrid particle swarm optimization for permutation flow shop scheduling problem with minimization of makespan.

Yi Sun, Min Liu, Chaoyong Zhang, Liang Gao and *Kunlei Lian*

N/A

N/A

In: IEEE International Conference in Industrial Engineering and Engineering Management, December 7, 2010.

### An effective hybrid genetic simulated annealing algorithm for process planning problem.

*Kunlei Lian*, Chaoyong Zhang, Xinyu Li and Liang Gao

N/A

N/A

In: Proceedings of the 5th International Conference on Natural Computation, August 14 – 16, 2009.


Talks {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------
### Study on a multi-objective periodic vehicle routing problem with service consistency

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

Philadelphia, PA

2015

- INFORMS Annual Meeting, (November 1 -- 4)

### Study on a multi-objective periodic vehicle routing problem with service consistency

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

Nashville, Tennessee

2015

- IIE Annual Conference & Expo (May 30 -- June 2)

### Vehicle routing problem with service consistency: a multi-objective approach

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

San Francisco, California

2014

- INFORMS Annual Meeting,  (November 9 -- 12)

### Study on home health care nursing routing problem

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

Montreal, Canada

2014

- IIE Annual Conference & Expo,  (May 31 -- June 3)

### Patient-focused considerations in	home health nursing routing problems

*Kunlei Lian*, Ashlea B. Milburn and Ronald L. Rardin

Minneapolis, Minnesota

2013

- INFORMS Annual Meeting,  (October 6 -- 9)

Journal Review {data-icon=binoculars}
--------------------------------------------------------------------------------

### Applied Soft Computing

number of reviews completed: 3

N/A

N/A

### Expert Systems with Applications

number of reviews completed: 1

N/A

N/A


### International Journal of Production Research

number of reviews completed: 9

N/A

N/A

### Journal of Heuristics

number of reviews completed: 3

N/A

N/A

###  Journal of Industrial and Production Engineering

number of reviews completed: 3

N/A

N/A


### Journal of Industrial Engineering International

number of reviews completed: 14

N/A

N/A


### Mathematical Problems in Engineering

number of reviews completed: 1

N/A

N/A

### Swarm and Evolutionary Computation

number of reviews completed: 2

N/A

N/A


### European Journal of Operational Research

number of reviews completed: 1

N/A

N/A

Awards {data-icon=award}
-------------------------------------------------------------

### IIE E.J. Sierleja Memorial Fellowship

N/A

University of Arkansas

2015

### Graduate Fellowship

N/A

Huazhong University of Science and Technology

2009

### Academic Achievement Award

N/A

Huazhong University of Science and Technology

2009

### Master’s Thesis Award

N/A

Huazhong University of Science and Technology

2012

### Outstanding Graduate Student Award

N/A

Huazhong University of Science and Technology

2009
  
### Bachelor’s Thesis Award

N/A

Huazhong University of Science and Technology

2009

### Meritorious Winner of Mathematical Contest in Modeling

N/A

MCM: The Mathematical Contest in Modeling

2007




```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>

")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


